int-theory-vacc PCA analysis

### 2019-04-30 notebooks/s1s2-pca-analysis.Rmd
modeling updates

loadings %>%
  ggplot(aes(x=PC1, y = PC2, label=rownames(loadings))) +
  geom_point(color="red") +
  geom_text_repel() +
  theme_bw() +
  labs(title="Component Loadings")

loadings %>%
  ggplot(aes(x=PC1, y = PC3, label=rownames(loadings))) +
  geom_point(color="red") +
  geom_text_repel() +
  theme_bw() +
  labs(title="Component Loadings")

loadings %>%
  ggplot(aes(x=PC2, y = PC3, label=rownames(loadings))) +
  geom_point(color="red") +
  geom_text_repel() +
  theme_bw() +
  labs(title="Component Loadings")
```

@@

>>>>

loadings %>%
  ggplot(aes(x=PC1, y = PC2, label=rownames(loadings))) +
  geom_text_repel() +
  geom_point(color="red") +
  theme_bw() +
  labs(title="Component Loadings")

loadings %>%
  ggplot(aes(x=PC1, y = PC3, label=rownames(loadings))) +
  geom_text_repel() +
  geom_point(color="red") +
  theme_bw() +
  labs(title="Component Loadings")

loadings %>%
  ggplot(aes(x=PC2, y = PC3, label=rownames(loadings))) +
  geom_text_repel() +
  geom_point(color="red") +
  theme_bw() +
  labs(title="Component Loadings")
```

@@

Another thing worth considering is taht this isn't a "model" in any traditional sense. It's just a method of compressing and reconstructing the data. So in the predictions for s1, it's not really "predicting " each variable without being given any data on that specific variable. Instead, it's being given all the variables, then compressing them, then seeing if it can reconstruct them, but the values for, e.g., vaccine intentions are used to create the compressed components that are used in the reconstruction, so it's not really an out-of-sample "prediction" in the same way that the bayesian network (or regression models) are doing.
